RadLib: a radiative heat transfer model library for CFD

### 2021-04-07 submissions/CPC_response_to_reviewers.md

## Reviewer 1

This manuscript introduces “RadLib,” a C++ library to calculate absorption coefficients for use in radiative heat transfer calculations. The library has reasonable value to the research community, despite a few limitations in its scope and design. The library is self-contained (doesn’t have any external dependencies), which is convenient.

I have a number of comments on the manuscript as well as the software itself which the authors should consider to improve the manuscript and software.

**The authors would like to thank the reviewer for their time and knowledge. While we disagree with some of the reviewer's comments and suggestions, they are, overall, constructive and helpful to the paper's development.**

### Manuscript:

1. There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.

	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.**

@@

9. Documentation:
    1.	Generating the documentation directly via doxygen v. 1.8.20 gives numerous warnings about obsolete tags and then fails because it is looking for a relative path “../../docs/doxygen” that doesn’t exist. This should be fixed.
    1.	Generating the doxygen documentation via the build system target (“make doxygen”) does seem to work fine.

## Reviewer 2

A radiation spectral property library is developed in this study using C++. A Planck-mean absorption coefficient based model, a WSGG model and a RCSLM model from the literature are implemented  in the package. Verification results are presented and discussed. Although the authors addressed an important issue of radiation modeling, the contribution is marginal in the reviewer's opinion. No new models/methods are proposed in this study. As the authors correctly pointed out, the solver for radiative transfer equation is equally important, which is not included in the library. The coupling of a spectral model to a specific RTE solver, can have different levels of challenges depending on the combination. The design of the library doesn't really address any of the RTE-related issues, nor provide any new solutions to simplify the coupling of spectral models to RTEs. If the authors can demonstrate that the library can be coupled with popular CFD software and popular RTE solvers such as P1 and DOM, it would further improve the quality of this study. A few other concerns are listed as follows:

**The authors would like to thank the reviewer for their comments and suggestions. We have already begun working on coupling RadLib to CFD software (that includes a DOM model for the RTE solution, among other features) in order to demonstrate RadLib's capabilities.**

**TO DO: couple RadLib to ODT for demonstration purposes**

@@

## Reviewer 3

The Computer Program in Physics (CPiP) submission titled, "RadLib: a radiative heat transfer model library for CFD" by Stephens et al reports a library of radiative property models that is modular and can be interfaced with other radiation model components. The manuscript is well-written and well-organized. The works cited are reasonable. RadLib contains a gray Planck-mean (PM) model, a weighted sum of gray gases (WSGG) model, and the rank-correlated SLW model. This is definitely an important tool for the combustion community, where the radiation modeling is often oversimplified mainly because of the lack of readily available appropriate radiation model libraries! I am not aware of any open-source libraries that combine the three property models presented here. The models included in RadLib are already well-established and well-validated in the radiation community. The library is written in C++ and is supposed to work in any Linux-like system. The code is well commented, although the associated documentation needs to be improved (see major comment #1).

Considering all these, I think that this CPiP submission is definitely within the scope of the journal and of interest to the research community. However, the following concerns must be addressed before the submission is considered for publication.

**The authors would like to thank the reviewer for their insightful comments and suggestions. As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**

@@

2) The library includes PM, one WSGG, and a RCSLW model. The authors should clearly indicate the rationale of these choices (i.e., why only these three models) early on in the manuscript. Since this is intended for researchers who, presumably, are not experts in radiation modeling, the inclusion of these three models can be misleading. One might think that these three models are the most appropriate models for their simulations.

**TO DO: add something to introduction to address this**

3) RadLib is intended to be expanded with new radiation property models in the future and interfaced with a user-supplied solver module for RTE. A brief discussion on how to interface such an external solver module should be presented. There is an example of a ray-tracing solver presented in the code files, but a brief discussion on coupling one's own RTE solver is important in the manuscript. Additionally, a brief discussion on how a user can add a new radiative property model should also be included.

	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.**

	**TO DO: add discussion and/or documentation on how to add new property models**

@@

6) In lines 48-52 on Page 4, the authors say that the absorption coefficients are calculated using some correlations after some curve-fitting to spectroscopic databases. I am not sure what the authors refer to as correlations. There may be some correlations involved in WSGG models, but it is not clear to me where are correlations involved in RCSLW.

	**The RCSLW model's key tool is the absorption line blackbody distribution function (ALBDF), which is calculated using sppectral data available from databases like HITEMP. This is discussed briefly at the end of Section 2.3 on pages 8-9. For more information on how spectral data is used to calculate the ALBDFs, please see reference [22].**

7) On page 7, the authors mention that the PM model can be "reasonably accurate" in some cases and go on to say that, "The Planck Mean model is most appropriate under optically thin conditions  with  relatively  low  radiative  transfer  relative  to  other  heat  sources such  as  reactive  heat  release  rates." The Planck Mean model will be appropriate in optically thin cases as there is very little reabsorption. This may or may not be connected with "relatively  low  radiative  transfer  relative  to  other  heat  sources." In fact, if the radiative heat transfer is much lower than chemical heat release, neglecting radiation altogether may also be reasonable! Although, the definition of "relatively low" is subjective.

	**These statements regarding PM absorption coefficients are generally true. In combustion simulations, low radiative heat transfer relative to other heat sources, including chemical heat release and convective heat transfer, usually does, in fact, indicate very low radiative reabsorption rates. Sectiom 2.1 has been revised to clarify this connection. The quoted sentence now reads as follows: "The Planck Mean model is most appropriate under optically thin conditions in which low radiative transfer relative to other heat sources, including but not limited to chemical heat release and buoyancy-driven convection in combustion systems, indicates that very little radiative reabsorption is occuring."**

	**The reviewer may be interested to know that there are, in fact, numerous computational studies of combustion systems in which radiative heat transfer is entirely neglected on the basis that it is overwhelmed by or insignificant compared to reactive and/or convective heat release. This is typically only true of highly controlled systems and/or combustion fuels consisting of small gaseous hydrocarbons like H2 and CH4 and few impurities. Because their parameters and boundary conditions are well-characterized, such systems are common in "canonical flame" libraries that comprise many of the validation targets used in combustion CFD. Most practical and everyday combustion systems, however, are neither highly controlled nor dependent on simple fuels---wildfires, coal and biomass fueled processes, and oxy-fired combustion, among other things, come to mind---and such justifications for neglecting or simplifying radiation treatments become increasingly tenuous. The phrase "relatively low" is indeed subjective, and it is liberally applied in the field of computational combustion. We, the authors, created and now present RadLib as a tool that can, ideally, enable researchers to apply more appropriate radiation modeling to simulation studies that might otherwise rely on such subjective assumptions. The paper touches on these ideas in the introduction and discussion sections, but does not go into detail for the sake of brevity.**

@@

8) On the same page, lines 40-41, "This version of  the  WSGG  model  is  advantageous  because  it  allows  for  arbitrary  CO2 and  H2O  compositions,  increasing  its  accuracy  and  flexibility." Can the authors provide some references that show the increased accuracy and/or flexibility of this WSGG over any other WSGG?

	**Two references for the chosen WSGG model are given earlier in the paragraph. The second (Bordbar et al. 2020) includes detailed comparisons between this model, its immediate predecessor (see Bordbar et al. 2014), five other WSGG models, and line-by-line calculations for four different test cases that show high accuracy over a wide range of molar ratio values. While other models may have performed better in individual tests, this model demonstrated consistent accuracy over a range of scenarios. For clarity, this reference has been added to the end of the aforementioned sentence so as to better indicate where to obtain relevant information.**

10) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?

	**This is correct. The molar ratio was defined using these variables by Bordbar et al. [10,11] for the WSGG model and have been retained for consistency.**

### 2021-04-07 submissions/CPC_response_to_reviewers.md

11) In lines 29-30 on page 13, please insert the units for Q in -80 and 200.

	**Appropriate units have been added to the specified values.**

12) In the Discussion (page 16), the authors write, "Neglecting radiation or using simple models like the optically thin assumption is adequate for some cases with simple geometry or limited chemical reactions…" This can be misleading. I am not sure if either the simple geometry or the limited chemical reactions give any indication of the importance of radiation. Rather, something like a radiant fraction or optical thickness may be a more appropriate metric to justify neglecting radiation or using an optically thin model.

	**This issue was partially addressed in the discussion above (see point 7). In combustion simulations, things like simple geometry and small domain sizes limit the extent of any chemical heat release or convective heat transfer, which usually indicates that radiative heat transfer plays a more prominent role than it would otherwise. In order to clarify this association, the sentence in question has been revised to read as follows: "Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results."**

### 2021-04-07 manuscript/manuscript.tex
Revisions to address reviewer comments on clarity

Planck Mean absorption coefficients are commonly used to model radiation, especially in combustion systems, because the model is relatively easy to implement, computationally inexpensive, and reasonably accurate in some cases. The Planck Mean model is most appropriate under optically thin conditions with relatively low radiative transfer relative to other heat sources such as reactive heat release rates. In cases where the optically thin assumption applies, such as simple hydrogen jet flames, this model and the associated Planck Mean absorption coefficients can produce accurate results \citep{Barlow_1999}. In cases where the optically thin assumption is not reasonable, including many other combustion scenarios, the Planck Mean model does not produce accurate results. For example, it significantly overpredicts radiative losses from the TNF library's CH$_4$ flames \cite{Frank_2000,Zhu_2002,Coelho_2002}. The examples included with the code and illustrated in Section \ref{s:Examples} demonstrate the deficiencies of the Planck Mean model in comparison to the others included with RadLib.

@@

Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs. Neglecting radiation or using simple models like the optically thin assumption is adequate for some cases with simple geometry or limited chemical reactions, but most simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results. In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error. Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.

>>>>

Planck Mean absorption coefficients are commonly used to model radiation, especially in combustion systems, because the model is relatively easy to implement, computationally inexpensive, and reasonably accurate in some cases. The Planck Mean model is most appropriate under optically thin conditions in which low radiative transfer relative to other heat sources, including but not limited to chemical heat release and buoyancy-driven convection in combustion systems, indicates that very little radiative reabsorption is occuring. In cases where the optically thin assumption applies, such as simple hydrogen jet flames, this model and the associated Planck Mean absorption coefficients can produce accurate results \citep{Barlow_1999}. In cases where the optically thin assumption is not reasonable, which includes most practical combustion scenarios of interest to engineers, the Planck Mean model does not produce accurate results. For example, it significantly overpredicts radiative losses from the TNF library's CH$_4$ flames \cite{Frank_2000,Zhu_2002,Coelho_2002}. The examples included with the code and illustrated in Section \ref{s:Examples} demonstrate the deficiencies of the Planck Mean model in comparison to the others included with RadLib.

@@

Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs. Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results. In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error. Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.
